### 2014-04-16 doc/uist14/iteration3.tex
further edited technique

\subsection{Technique}
Using the motion sensors (including gyroscope, magnetometer and accelerometer) on the
head-worn device and IR, we can discover the spatial relationships between targets and the head orientation of the user.

Unfortunately, this absolute orientation cannot be applied to all indoor
environments, since the user’s movements through the space could change the relationships between targets. However, with the constraint that the targets are spread around the periphery, their relative orientations are stable
(see Figure~\ref{fig:third_principle}). This key observation inspires us to
investigate a hybrid solution using a combination of IR and orientation sensors on Glass.

@@

There are two phases to this technique: learning the relative orientations or
targets in a room and intelligently suggesting targets during refinement (see
Figure~\ref{fig:third_technique}).

>>>>

\subsection{Technique}

We introduce a third technique that uses a combination of motion sensors and IR to learn the relative orientations of
targets in a room and intelligently suggest targets during refinement (see
Figure~\ref{fig:third_technique}).

Unfortunately, this absolute orientation cannot be applied to all indoor
environments, since the user’s movements through the space could change the relationships between targets. However, with the constraint that the targets are spread around the periphery, their relative orientations are stable
(see Figure~\ref{fig:third_principle}).

@@
